Final Report Semester Project

### 2018-12-13 Final /Draft Visualizations Template.Rmd
Final package chnages

```{r}
#Create visualization
AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Is your anonymity protected?") + ylab("Count")+ theme(axis.title=element_text(size=12))
AnoymityPolicies_By_CompanySize_Viz
```

>>>>

```{r}
#Create visualization
AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
AnoymityPolicies_By_CompanySize_Viz
```
